Analysis of competitive surfing tournaments with generalized Bradley-Terry likelihoods

### 2022-09-25 inst/surfing_jsa_rebuttal_minorcomments.tex

\textcolor{blue}{The referee is quite right: Vries competed only twice
  in 2019, coming last (second and third) in each of his two sessions.
  Brief explanation added to he mauscript.}

Page 6 / Figure 1: I'm pleased to see the authors replace the old pie
chart in Figure 1 with a dot chart---this is a much clearer
visualization of the results.  On Page 6 the authors state: ``Figure 1
shows the maximum likelihood estimate for the 23 competitors'
strengths, which appears to show a wide range from Florence at about
$17.5\%$ down to Morais at about $1\%$". What exactly do the
quantities $17.5\%$ and $1\%$ refer to/how are they computed? A quick
clarification of these quantities would help explain the practical
implications of the findings.

\textcolor{blue}{The figures are, as stated, the maximum likelihood
  estimates of the competitors' strengths.  We think that our use of
  percentages (which add to 100) instead of strengths (which add to 1)
  was the cause of the confusion and we have amended the manuscript to
  use strengths, not percentages.}

Page 7/Figure 2: The authors suggest there is a loose positive
correlation between maximum likelihood strength and total points,
which is undoubtedly true. However, the x-axis on Figure 2 itself has
been distorted, which makes the trend appear more linear than it
really is. I'd prefer to see the x-axis undistorted, unless the
authors are explicitly trying to make a point about the trend being
log-linear, in which case I'd like to see this briefly discussed.

\textcolor{blue}{Horizontal axis now linear; no other change except
  for tiny movement of labels so they do not obscure one another.  We
  are mortified to see that the linearity is more apparent without the
  log-transform.}

Page 7: The authors suggest we may reject the hypothesis that the strength of the entity exceeds
about 0.025. Does this assertation come with a supporting p-value? It is unclear from Figure 4 how
this conclusion is reached.

### 2022-09-25 inst/surfing_jsa.tex
fixes #171

\begin{figure}[h]
  \includegraphics[width=4in]{directlogplotofstrengths_postinkscape.pdf}  % to create this file, open directlogplotofstrengths_postinkscape.svg in inkscape and export to PDF.  File directlogplotofstrengths_postinkscape.svg is under version control in the hyper2 github repo.  It is a slight modification of directlogplotofstrengths.pdf, with slight optical glitches removed.  File directelogplotofstrengths.pdf is produced by surfing.Rmd.
\caption{Scatterplot of points scored  \label{compare_likelihood_points}
against maximum likelihood estimates}
\end{figure}

>>>>

%\begin{figure}[h]
%  \includegraphics[width=4in]{directlogplotofstrengths_postinkscape.pdf}  % to create this file, open directlogplotofstrengths_postinkscape.svg in inkscape and export to PDF.  File directlogplotofstrengths_postinkscape.svg is under version control in the hyper2 github repo.  It is a slight modification of directlogplotofstrengths.pdf, with slight optical glitches removed.  File directelogplotofstrengths.pdf is produced by surfing.Rmd.
%\caption{Scatterplot of points scored  \label{compare_likelihood_points}
%against maximum likelihood estimates}
%\end{figure}

%\clearpage
%\newpage

\begin{figure}[h]
  \includegraphics[width=4in]{directplotofstrengths_postinkscape.pdf}  % to create this file, open directplotofstrengths_postinkscape.svg in inkscape and export to PDF.  File directplotofstrengths_postinkscape.svg is under version control in the hyper2 github repo.  It is a slight modification of directplotofstrengths.pdf, with slight optical glitches removed.  File directplotofstrengths.pdf is produced by surfing.Rmd.
\caption{Scatterplot of points scored  \label{compare_likelihood_points}
against maximum likelihood estimates}
\end{figure}
